### 2023-12-13 latex/Plusone_configs/paper.tex
#27 Paper

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}
The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
\\Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. At time $t$,
we can view lots of VIX futures contracts with different expiration dates:
\begin{eqnarray}
    \mathrm{F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
\end{eqnarray}
where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
a linear interpolation of two nearest expiration dates VIX futures:
\begin{eqnarray}
\label{eq:defineV}
    \mathrm{V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
\end{eqnarray}
where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
$\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
CMFs are commonly used for they do not suffer fluctuations caused by contract expiry.

\subsubsection*{Rolling VIX Futures Derivatives and Strategies}
Through a rolling VIX futures derivatives or strategies can reappearance the daily returns of CMFs.
SPVXSP, SPVIX2ME, SPVIX3ME, SPVIX4ME, SPVXMP, SPVIX6ME represents 1-6 months CMFs, they can be traded or replicated with trades in the rolling VIX futures strategies.
Derivatives like ETFs and ETNs or Strategies maintains the CMF weights of equation \ref{eq:define V} for fixed maturity $j-month$. For each $j$, we denote $R^j$
the daily return of rolling VIX futures strategy, trading cost is not considered:
\begin{eqnarray}
    \mathrm{R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
\end{eqnarray}
where${\Delta}F^{L_j}_t = F^{L_j}_{t+1} - F^{L_j}_t$. We denote ${\Delta}t = \frac{1}{252}$, transform equation in terms of the CMFs:
\begin{eqnarray}
\label{eq: $R^j_t$2}
    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
\end{eqnarray}
Let Roll denote the drift term in equation \ref{eq: $R^j_t$2}, it referred to as the roll yield of rolling VIX futures strategy:
\begin{eqnarray}
    \mathrm{Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
\end{eqnarray}
In a Contango circumstances, $F^{R_j}_{t+1} > F^{L_j}_{t+1}$ means $Roll < 0$. On the opposite, in a Backwardation circumstances $Roll > 0$.
We re-write equation as follows:
\begin{eqnarray}
\label{eq: $R^j_t$3}
    \mathrm{R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
\end{eqnarray}
From equation \ref{eq: $R^j_t$3} we see $R^j_t$ consist of two parts, the change in $V^j_t$ and roll yield. As history data shown, the most likely VIX futures
curves are contango, so the value of the rolling VIX futures strategies decay.
\\xxx shows that volatility is a mean-reversion process, in a ideal world, suppose $V^j_t$ and CMFs are both stable for a long time like a month, then
the return of $V^j_t$ should be $V^j_t - V^{j-1}_t$, so we denote $\mu$ as :
\begin{eqnarray}
\label{eq: mu}
    \mathrm{\mu^j_t} = V^j_t - V^{j-1}_t
\end{eqnarray}
$\mu^j_t$ contains instantaneous market views of return about $V^j_t$.
ynorm

@@

\subsubsection*{2.3 Recurrent Neural Network (RNN)}
We then implement multiple machine learning models based on RNN architecture which aims to find patterns in sequences of data. The work of Schmidt (2019) provides a comprehensive overview of the basic architecture and functions of RNNs while \textit{Sherstinsky (2023) work focuses on deriving the classical RNN formulation from differential equations and addresses the challenges in training standard RNNs. The transformation of RNN into the "Vanilla LSTM" network is explained through logical arguments, with a detailed description of the LSTM system's equations and entities. }

@@

Eq.2 and eq.3 illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.

[eq.2], [eq.3]

@@

[eq.4]

@@

[eq.5]

@@

[eq.6]
\section*{data and experiment design}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

>>>>

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}
The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
\\Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. At time $t$,
we can view lots of VIX futures contracts with different expiration dates:
\begin{eqnarray}
    {F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
\end{eqnarray}
where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
a linear interpolation of two nearest expiration dates VIX futures:
\begin{eqnarray}
\label{eq:defineV}
    {V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
\end{eqnarray}
where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
$\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
CMFs are commonly used for they do not suffer fluctuations caused by contract expiry.

\subsubsection*{Rolling VIX Futures Derivatives and Strategies}
Through a rolling VIX futures derivatives or strategies can reappearance the daily returns of CMFs.
SPVXSP, SPVIX2ME, SPVIX3ME, SPVIX4ME, SPVXMP, SPVIX6ME represents 1-6 months CMFs, they can be traded or replicated with trades in the rolling VIX futures strategies.
Derivatives like ETFs and ETNs or Strategies maintains the CMF weights of equation \ref{eq:define V} for fixed maturity $j-month$. For each $j$, we denote $R^j$
the daily return of rolling VIX futures strategy, trading cost is not considered:
\begin{eqnarray}
    {R^j_t} = \frac{\omega^j_t{\Delta}F^{L_j}_t\ + (1 - \omega^j_t){\Delta}F^{R_j}_t}{\omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t}
\end{eqnarray}
where${\Delta}F^{L_j}_t = F^{L_j}_{t+1} - F^{L_j}_t$. We denote ${\Delta}t = \frac{1}{252}$, transform equation in terms of the CMFs:
\begin{eqnarray}
\label{eq: $R^j_t$2}
    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}{\Delta}t
\end{eqnarray}
Let Roll denote the drift term in equation \ref{eq: $R^j_t$2}, it referred to as the roll yield of rolling VIX futures strategy:
\begin{eqnarray}
    {Roll^j_{t+1}} := - \frac{F^{R_j}_{t+1} - F^{L_j}_{t+1}}{V^j_t(T_{R_j} - T_{L_j}){\Delta}t}
\end{eqnarray}
In a Contango circumstances, $F^{R_j}_{t+1} > F^{L_j}_{t+1}$ means $Roll < 0$. On the opposite, in a Backwardation circumstances $Roll > 0$.
We re-write equation as follows:
\begin{eqnarray}
\label{eq: $R^j_t$3}
    {R^j_t} = \frac{{\Delta}V^j_t}{V^j_t} + Roll^j_{t+1}{\Delta}t
\end{eqnarray}
From equation \ref{eq: $R^j_t$3} we see $R^j_t$ consist of two parts, the change in $V^j_t$ and roll yield. As history data shown, the most likely VIX futures
curves are contango, so the value of the rolling VIX futures strategies decay.
\\xxx shows that volatility is a mean-reversion process, in a ideal world, suppose $V^j_t$ and CMFs are both stable for a long time like a month, then
the return of $V^j_t$ should be $V^j_t - V^{j-1}_t$, so we denote $\mu$ as :
\begin{eqnarray}
\label{eq: mu}
    {\mu^j_t} = V^j_t - V^{j-1}_t
\end{eqnarray}
$\mu^j_t$ contains instantaneous market views of return about $V^j_t$.
ynorm

@@

\subsubsection*{2.3 Recurrent Neural Network (RNN)}
We then implement multiple machine learning models based on RNN architecture which aims to find patterns in sequences of data. The work of Schmidt (2019) provides a comprehensive overview of the basic architecture and functions of RNNs while \textit{Sherstinsky (2023) work focuses on deriving the classical RNN formulation from differential equations and addresses the challenges in training standard RNNs. The transformation of RNN into the "Vanilla LSTM" network is explained through logical arguments, with a detailed description of the LSTM system's equations and entities. }
RNN train a function $f$:
\begin{eqnarray}
\label{eq: RNN}
    {h_{t}, y_t} = f(h_{t - 1}, x_t)
\end{eqnarray}
where $h$ represents hidden layer, it carry sequence information by $t - 1$, $x_t$ is the input at $t$, $f$ outputs result $y_t$ at $t$ and sequence information $h_t$.

@@

Eq \ref {eq: LSTM} and Eq \ref {eq: ALSTM} illustrates the mathematical details for the implementation of LSTM and ALSTM in our study.
LSTM framework denote $c$ as the long-term sequence information distinguish from $h$, and design gates to filter information. A gate cell can be represent as:
\begin{eqnarray}
\label{eq: Gate}
    g = \sigma(W\bullet[h_{t - 1}, x_t] + b)
\end{eqnarray}
where $W, b$ are trainable parameters, $\sigma$ represent activation function, so $g$ can be use as a gate. LSTM framework design three gate on RNN as follow:
\begin{eqnarray}
\label{eq: LSTM}
    \begin {cases} c_t = g^f{\odot}c_{t - 1} - g^i{\odot}tanh(W\bullet[h_{t - 1}, x_t] + b)
    \\h^t = g^o{\odot}tanh(c_t)
    \\y^t = f(h_t)
    \end {cases}
\end{eqnarray}
$g^f, g^i, g^o$ represent three gates, and $f$ is some function link LSTM outputs to downstream task.
\\ALSTM add a encoder and a decoder attention-based layers in LSTM, Given $n$ series, stage one encoder layer can learn attention at a same time and transform to new input.
\begin{eqnarray}
\label{eq: ALSTM1}
    \begin {cases} e^k_t = tanh(W\bullet[h_{t - 1}, c_{t - 1}] + bx^k)
    \\{\alpha}^k_t = \frac{exp(e^k_t)}{\sum_{i=1}^n exp(e^i_t)}
    \\\widetilde{x_t} = ({\alpha^1_t}x^1_t, {\alpha^2_t}x^2_t,..., {\alpha^n_t}x^n_t)
    \end {cases}
\end{eqnarray}
with $\widetilde{x_t}$ as input, stage one construct with a LSTM framework named $L_1$, stage two decoder layer learn attention with all the hidden state $h_t$ of $L_1$,
the output $\widetilde{h_t}$ transform the label $y$ of another LSTM framework named $L_2$, so two attention layers can learn relations between $n$ series.
Let $d$ denote the hidden state of $L_2$, transform of $y$ can be formulate as:
\begin{eqnarray}
\label{eq: ALSTM2}
    \begin {cases} l_t = tanh(W\bullet[d_{t - 1}, c^2_{t - 1}] + bh^i)
    \\{\beta}_t = \frac{exp(l_t)}{\sum_{i=1}^T exp({\beta}_t)}
    \\c_t = \sum_{i=1}^T {\beta}_ih_i
    \\\widetilde{y_{t - 1}} = W\bullet[y_{t - 1}; c_{t - 1}] + b
    \end {cases}
\end{eqnarray}
$\tilde{y}$ is the input of $L_2$.

@@

\begin{eqnarray}
\label{eq: GRU}
    \begin {cases} h^{'}_{t - 1} = h_{t - 1}{\bullet}g^r
    \\h^{'} = tanh(W\bullet[h^{'}_{t - 1}, x_t] + b)
    \\h^t = (1 - g^z){\odot}tanh(c_t) + g^z{\odot}h^{'}
    \end {cases}
\end{eqnarray}
Follow notation in LSTM,  $g$ represents gate \ref{eq: Gate}.

@@

\begin{eqnarray}
\label{eq: TCN}
    TCN = FCN + \text{causal convolutions}
\end{eqnarray}
where FCN is fully-convolutional network with one dimension.

@@

\begin{eqnarray}
\label{eq: Transformer}
    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
\end{eqnarray}
In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
\begin{eqnarray}
\label{eq: TransformerDecoder}
    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
    \\Y = FFN(\text{self-attention}(X))
    \end {cases}
\end{eqnarray}
where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
\begin{eqnarray}
\label{eq: self-attention}
    \begin {cases} Q = W^QX
    \\K = W^KX
    \\V = W^VX
    \\Z = \test{softmax}(QK^T)V
    \end {cases}
\end{eqnarray}
where $Z$ is the output of self-attention layer.

\section*{data and experiment design}
\subsubsection*{Data Preparations}
In line with our primary goal of predicting next-day arithmetical return of \(CMFs\) as denoted in eq.X, it is rational to initially incorporate CMFs-related factors \(V^j_t\) and \(Roll^j_{t+1}\) as detailed in Eq.2 and Eq.5. Additionally, to thoroughly examine the informative power of term structures, we introduce \(\mu^j_t\) denoted in Eq.7 and \(\triangle Roll_{t}^j\)to provides a comprehensive description of the CMFs term structure. We also integrate \(TLT\) and \(SPY\) into our analysis to partially represents the macro-economics conditions. Furthermore, various time-series statistical transformations are employed to explore possible extra information with details provided in table 3. The time range for \(VIX\)  futures and \(CMFs\)  data covers the period from January 3, 2005, to March 7, 2023 while \(TLT\)  and \(SPY\)  data are selected within the time frame of January 12, 1995, to April 12, 2023. Three distinct data sets are utilised to incrementally examine the informative power of VIX term structures and additional information offered by time-series statistical transformations.
Detailed descriptions of all three datasets are provided in tables 1, 2 and 3.
\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Simple Data sets}}
\begin{tabular}{|c|c|c|} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
    \hline % Horizontal line at the top
    \(VIX_{CMFs}\)  & CMFs-related factors & Macro-factors \\
    \hline % Horizontal line under column headers
    \(CMF_{1m}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
    \hline
    \(CMF_{2m}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
    \hline
    \(CMF_{3m}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
    \hline
    \(CMF_{4m}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\)\\
    \hline
    \(CMF_{5m}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
    \hline
    \(CMF_{6m}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) \\
    \hline % Horizontal line at the bottom
  \end{tabular}
\begin{flushleft} Table notes: The initial data sets comprise solely of CMFs-related factors and macroeconomic variables.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Term Structure Data sets}}
\begin{tabular}{|c|c|c|c|c|c|} % Use c for centered columns; you can also use other alignment options like l (left) or r (right)
    \hline % Horizontal line at the top
    \(VIX_{CMFs}\)  & CMFs-related factors & Macro-factors & Term Structures factors \\
    \hline % Horizontal line under column headers
    \(CMF_{1m}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^1, \triangle Roll_{t}^1]}\)  \\
    \hline
    \(CMF_{2m}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) &  \({[\mu_{t}^2, \triangle Roll_{t}^2]}\) \\
    \hline
    \(CMF_{3m}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^3, \triangle Roll_{t}^3]}\) \\
    \hline
    \(CMF_{4m}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^4, \triangle Roll_{t}^4]}\)\\
    \hline
    \(CMF_{5m}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^5, \triangle Roll_{t}^5]}\) \\
    \hline
    \(CMF_{6m}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^6, \triangle Roll_{t}^6]}\)  \\
    \hline % Horizontal line at the bottom
  \end{tabular}
\begin{flushleft} Table notes: Term structures have been added to the data sets based on the simple datasets.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{sidewaystable}
\caption{{\bf Statistical Derivations Data Sets}}
%\begin{adjustwidth}{2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\begin{tabular}{|c|c|c|c|c|c|}% Use c for centered columns; you can also use other alignment options like l (left) or r (right)
    \hline % Horizontal line at the top
    \(VIX_{CMFs}\)  & CMFs-related Factors & Macro-factors & Term Structure Factors & Time-series Statistical Derivations\\
    \hline % Horizontal line under column headers
    \(CMF_{1}\)  & \({[V_{t}^1},{Roll_{t}^1]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^1, \triangle Roll_{t}^1]}\) &
    \makecell[c]{\([Std_{T}(All_{t}^{1}), Skew_{T}^{1}(All_{t}^{1}),Kurt_T(All_{t}^{1}),Mean_{T}(All_{t}^{1})\),\\ \(z\ score_{T}(term_{t}^{1})\)\\ , \(where \: T \in \{5,20, 60\}\)]}   \\
    \hline
    \(CMF_{2}\)  & \({[V_{t}^2},{Roll_{t}^2]}\)  & \([log_{SPY_t},log_{TLT_t},VIX_t]\) &  \({[\mu_{t}^2, \triangle Roll_{t}^2]}\) &   \makecell[c]{\([Std_{T}(All_{t}^{2}), Skew_{T}^{2}(All_{t}^{2}),Kurt_T(All_{t}^{2}),Mean_{T}(All_{t}^{2})\),\\ \(z\ score_{T}(term_{t}^{2})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
    \hline
    \(CMF_{3}\)  & \({[V_{t}^3},{Roll_{t}^3]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^3, \triangle Roll_{t}^3]}\) &  \makecell[c]{\([Std_{T}(All_{t}^{3}), Skew_{T}^{3}(All_{t}^{3}),Kurt_T(All_{t}^{3}),Mean_{T}(All_{t}^{3})\),\\ \(z\ score_{T}(term_{t}^{3})\)\\ , \(where \: T \in \{5,20, 60\}\)]}  \\
    \hline
    \(CMF_{4}\)& \({[V_{t}^4},{Roll_{t}^4]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^4, \triangle Roll_{t}^4]}\) &   \makecell[c]{\([Std_{T}(All_{t}^{4}), Skew_{T}^{4}(All_{t}^{4}),Kurt_T(All_{t}^{4}),Mean_{T}(All_{t}^{4})\),\\ \(z\ score_{T}(term_{t}^{4})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
    \hline
    \(CMF_{5}\) &  \({[V_{t}^5},{Roll_{t}^5]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^5, \triangle Roll_{t}^5]}\) &  \makecell[c]{\([Std_{T}(All_{t}^{5}), Skew_{T}^{5}(All_{t}^{5}),Kurt_T(All_{t}^{5}),Mean_{T}(All_{t}^{5})\),\\ \(z\ score_{T}(term_{t}^{5})\)\\ , \(where \: T \in \{5,20, 60\}\)]} \\
    \hline
    \(CMF_{6}\) & \({[V_{t}^6},{Roll_{t}^6]}\) & \([log_{SPY_t},log_{TLT_t},VIX_t]\) & \({[\mu_{t}^6, \triangle Roll_{t}^6]}\) & \makecell[c]{\([Std_{T}(All_{t}^{6}), Skew_{T}^{6}(All_{t}^{6}),Kurt_T(All_{t}^{6}),Mean_{T}(All_{t}^{6})\),\\ \(z\ score_{T}(term_{t}^{6})\)\\ , \(where \: T \in \{5,20, 60\}\)]}  \\
    \hline % Horizontal line at the bottom
\end{tabular}
\begin{flushleft} Table notes: \( All_{t}^{j} \in \{CMFs\ related \ Factors, Macro \ factors, Term\ Structure\ Factors\}\) and \(term_{t}^{j} \in \{Term\ Structure\ Factors \}\)

\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{sidewaystable}

 \subsubsection*{Empirical Experiment Designs}
 The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets.
Before training we are dealing with tabular datasets with multi-index datetime and instruments, columns represents features. we form dataset {(Xi, yi)}i=1,2,..,I into a single combined dataset(X, y) to train model instead of train I models every task named "features stacking". With this dataset organization, conclusions are more general and less biased by outliers or over fitting and model can be trained with more data, correspondingly correlation of instruments are not considered in the model.

\subsubsection*{Trading Strategy: A mean-variance approach}
To ascertain optimal portfolio weights grounded in forecasted data, we employed mean-variance optimization incorporating additional constraints. The covariance structure was derived through the estimation of a 60-day historical covariance matrix. The risk aversion parameter, denoted as gamma, was fixed at a value of 0.2.
To ensure prudent risk management, we imposed constraints on portfolio characteristics. Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of VIX futures indices, ensuring they did not exceed an absolute value of 1. Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30%.
This methodology, integrating forecast-driven optimization within a risk-constrained mean-variance framework, provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation. The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy.

Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.
